Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-07-27 Final_Manuscript.Rmd
added some to discussion

Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US. The description of the samples section below contains more detail about equivalence analyses to support the decision to combine these two samples.

@@

###Description of the Samples
Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study.  More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college. Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals. Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2. For consistency, we limited participant data to same sex female pairs at the two colleges.

@@

#Discussion

>>>>

Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from two liberal arts institutions in the Northeast of the United States participated in this study. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US. More specifically, twelve of the pairs, which derived from Sample 1, were students at a co-ed liberal arts college, while the remaining twenty pairs who came from Sample 2 attended a women’s liberal arts college. Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals. Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2. For consistency, we limited participant data to same sex female pairs at the two colleges.

@@

@@

#Discussion
The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only. Although past reserach has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if this other-objectification by women is related to self-objectification in women. As hypothesized, the current study did find a significant relationship bewteen a woman's partner's report of having objectified her and her own post-interaction feelings of self-objectification.

Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and felt inauthenticity [@garcia2016objectification]. In addition, we found to evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations. Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes. This is somewhat suprising given the extant research on interpersonal other-ojectification and cognitive functioning [CITE that logel study], and the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; CITE; CITE; CITE]. This lack of evidence could potentially signal diverging processs between women's experiences with interpersonal objectification from men and interpersonal objectification from women. There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [CITE; CITE; CITE], and perhaps the self-objectification experienced within an interaction with a women is not as detrimental as the self-objectificatoin experienced within an interaction with a man. This lack of evidence could also be due to the relatively small sample size.

What we did find, however,
